---
title: "Create_shapefiles_for_field_trial_plots"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(root.dir = "/analysis/weed_detectionAHRI/field_trial")
```

Load the required libraries
```{r }
library('dplyr')
library('tidyr')
library('UAStools')
library('readxl')
```

Following the instructions from the original tutorial https://github.com/andersst91/UAStools/wiki/plotshpcreate.R#ex1-single-row-plots

The only important columns are "Range, Row, Plot, Barcode". The fieldnotes can be uploaded directly after confirming the columns are properly named.

```{r}
# Import the table files with experiment description
bl_infile <- read_excel('/analysis/weed_detectionAHRI/field_trial/fieldnotes.xlsx')
```

```{r}
# Select the required columns from the fieldnotes file
bl_infile <- bl_infile %>% 
  select(RANGE, ROW, Barcode, Plot)

# Rename the file
bl_test <- bl_infile
# Renamed the columns because the fieldnotes have the range and row for opposite directions. It is important to read the library documentation to know what the tool expects.
bl_test <- bl_test %>% rename(Range = ROW) %>% rename(Row = RANGE)

```

Coordinated easting, northing
(Can be obtained by opening the orthomosaic on QGIS)  

up_left =    344318.613803779,6751550.37374348
up_right =   344377.476175635,6751550.73430931
down_right = 344376.989411763,6751480.17157625
down_left =  344318.090983325,6751480.78453816

```{r}
plotshpcreate(A=c(344318.403803779,6751550.37374348),
              B=c(344377.476175635,6751550.73430931),
              infile = bl_test,
              nrowplot = 1,
              rangespc = 8,
              rangebuf = 0.5,
              rowspc = 40, 
              rowbuf = 3,
              outfile ='110821_shapefile',
              field='sandplain_field')
```

Should output multiple files, including shapefiles.


